---
title: "Assessment 1.1"
author: "Mungungerel s4647066"
date: "05/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

install.packages("tidyverse") 

#Rmarkdown editing

**_R Markdown turn the analyses into high quality documents, reports, presentation, and dashboards. Using knitr syntax we can write documents and embed executable R code chunks. To update the document re-knitting the code chunks will be used at any time. Moreover, it can be converted document into several common formats._**


[Rstudio](https://rmarkdown.rstudio.com/lesson-8.html)

```{r}

library(tidyverse)
```


### 6.Insert an R chunk and create a variable with this dataset
https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv


```{r}
fastfood<-read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")

```

### 7. Display the first 10 rows of the dataset. Use Help to see how you can do this with `head()` function.Display the first 10 rows of the dataset and the first 5 variables using kable() function 

```{r}
fastfood%>%head(10)

knitr::kable(head(fastfood[1:10,1:5]), "pipe")
```

### 8. Display the observations that has more than 1000 calories
```{r}
 fastfood%>%filter(calories>1000)
  
```

### 9. Save observations with more than 40 in total_fat and more than 80 in total_carb in a new variable (dataset) called `dont_eat_this`

```{r}
dont_eat_this<-fastfood
  dont_eat_this%>%filter(total_fat>40 & total_carb>80)
```
### 10. Using the initial dataset variable, display observations from restaurant Mcdonalds.

```{r}
fastfood%>%filter(restaurant=="Mcdonalds")
```

