---
title: "Assessment 1.1"
author: "Mungungerel s4647066"
date: "05/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Rmarkdown editing

**_R Markdown turn the analyses into high quality documents, reports, presentation, and dashboards. Using knitr syntax we can write documents and embed executable R code chunks. To update the document re-knitting the code chunks will be used at any time. Moreover, it can be converted document into several common formats._**


[Rstudio](https://rmarkdown.rstudio.com/lesson-8.html)

install.packages("tidyverse")
library(tidyverse)

```{r}
fastfood <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")

fastfood%>%head(10)
knitr::kable(head(fastfood[1:10,1:5]), "pipe")


  fastfood%>%filter(calories>1000)
  dont_eat_this<-fastfood
  dont_eat_this%>%filter(total_fat>40 & total_carb>80)
```


```{r}
fastfood%>%head()
```


#Part2
##Q11.
```{r}
install.packages("skimr")
install.packages("dplyr")
library(skimr)
summary(fastfood)
```
##Q12. Show the count of observations for each restaurant.


```{r}
library(tidyverse)
fastfood <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")
res_count%>%count(restaurant)  



```
#Q13. Using grouppings (group_by()), summarise and display the average number of calories for each restaurant.

```{r}

fastfood%>%
  group_by(restaurant)%>%
  summarise(mean(calories))

```

#Q14. Add a variable to the dataset, which calculates the average calories per type of restaurant and call it `average_calories`

```{r}
  average_calories<-
  fastfood%>%
  group_by(restaurant)%>%
  summarise(average_calories=mean(calories))
```


#Q15.  Display the data vis of total fat per each type of restaurant. Write a narration (2-3 sentences) why you believe this type of data viz presents such information best.
##I used geom_boxplot geometrical object to evaluate the highest value and lowest value as seen below. It can easily show the total data in two-dimensional way. 

```{r}
  library(ggplot2)
  fastfood%>%
  group_by(restaurant)%>%
  summarise(mean(total_fat))
 ggplot(data= fastfood, mapping = aes(x= restaurant, y=total_fat))+
   geom_boxplot()
 
```



#Q16. Add a variable to the dataset, which calculates the maximum total fat per type of restaurant and call it `max_total_fat`

  
```{r}
max_total_fat<-  
fastfood%>%
  group_by(restaurant)%>%
  summarise(max_total_fat=mean(total_fat))
```

#Q17. Use observations for Mcdonalds to plot sugar variable against protein with `geom_point()` 

```{r}
fastfood%>%
  filter(restaurant=="Mcdonalds") 
ggplot(data=fastfood, mapping = aes(x=sugar, y=protein)) +
  geom_point()
```

