---
title: "Assignment2"
output: html_document
---



## _Mungungerel_ , __s4647066__

_____

# Assignment 2

____
install.packages("tidyverse")
install.packages("ggplot2")
install.packages("knitr")

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

```



### Part 2: Data Wrangling and visualization 38 marks

### 1. Display the first 10 rows of the dataset using `kable()` function (1 marks). 

```{r}
thanks <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-11-20/thanksgiving_meals.csv")

library(knitr)
```

```{r}
kable(head(thanks[10,], "pipe"))

```

### 2.Using `skim()` display the summary of variables. 



```{r}
library(skimr)
summary(thanks)
skim(thanks)
```

### 3.Use `fct_reorder` and `parse_number` functions to create a factor variable `family_income`(2 mark).
```{r}

family_income<-
thanks$family_income<-factor(thanks$family_income)
fct_reorder(thanks$family_income, thanks$id)

```
### 4. What is the number of people who celebrate? (1 mark) 

```{r}
thanks %>%
  count(celebrate) %>% 
  filter(celebrate=="Yes") %>% kable()
```

### 5. What are categories and insights for each main dish served and the method it is prepared? (2 marks)

```{r}
thanks %>%
  count(main_dish, main_prep)%>% kable()

```
### 6. Create 3 different data viz showing insights for main dish served and the method. Provide your own legend and use themes.

```{r}
thanks %>%
  count(main_dish, main_prep, sort=TRUE) %>%
  ggplot(aes(main_dish,n, fill=main_prep)) +
  geom_col()+
  facet_wrap(main_prep~.)+
  coord_flip()+
  labs(x="Type of Main Dish", y="Number of items", title="Choose type of dish", caption="Image 1: Graph")+ 
    theme_linedraw()
```


### 7.How many use cranberry sauce? How many use gravy? 2 marks

```{r}

thanks %>% 
  count(cranberry) %>%
  filter(cranberry=="Canned" | cranberry=="Homemade")%>% kable()
```

```{r}
thanks %>%
  count(gravy)%>%
  filter(gravy=="Yes") %>% kable()

```


### 8.9. What is the distribution of those who celebrate across income ranges. Create a data viz.
```{r}
thanks%>%
  count(celebrate, family_income) %>%
  filter(celebrate=="Yes") %>%
  group_by(family_income) %>%
  ggplot(aes(family_income, n, fill=celebrate))+
  geom_col()+
  coord_flip()+
  labs(x="Income Range", y="Number of people", title = "Who want celebrate the Thanksgiving", caption = "Image 2:Graph") +
  theme_test()
```
### 10.What are the most common pies, sides, and desserts?

```{r}
thanks %>% select(starts_with("pie")) %>% gather(type,value) %>% count(value,sort = TRUE)%>%kable() 

```
```{r}

thanks %>% select(starts_with("side")) %>% gather(type,value)%>% count(value, sort = TRUE)   %>%kable()  
```



```{r}
thanks %>% select(starts_with("dessert")) %>% gather(type,value)%>% count(value, sort = TRUE)  %>%kable() 

```


  
### 11. Present this information on a data viz
```{r}
thanks %>% select(starts_with("pie")) %>% gather(type,value)%>% filter(!is.na(value)) %>% mutate(value = fct_lump(value,5)) %>% ggplot(aes(value))+geom_bar(fill="458964")+coord_flip()+theme_bw()+labs(title="Most Common Pie")

thanks %>% select(starts_with("side")) %>% gather(type,value)%>% filter(!is.na(value)) %>% mutate(value = fct_lump(value,5)) %>% ggplot(aes(value))+geom_bar(fill="458965")+coord_flip()+theme_bw()+labs(title="Most Common Side")

thanks %>% select(starts_with("dessert")) %>% gather(type,value)%>%filter(!is.na(value)) %>% mutate(value = fct_lump(value,5)) %>% ggplot(aes(value))+geom_bar(fill="#458963")+coord_flip()+theme_bw()+labs(title="Most Common Dessert")

```


### 13.14 How do the servings differ by income? Present this information on a data viz
```{r}
thanks %>% filter(main_dish !='None', main_dish!="Other (please specify)") %>% count(main_dish, family_income) %>%
  ggplot(aes(main_dish, n, color="red"))+
  geom_col()+
  facet_wrap(family_income ~.)+
  coord_flip()+
  geom_text(aes(label=round(n, digits=2)), vjust=-0.25, size=3, colour="blue")+
  theme(legend.position = "none")+
  labs(x="Dishes Type", y="Frequency of how those dishes are prepared", title="The most common way some Thanks Giving dishes are preprared", caption = "Graph type: Point")
```


